\magnification=1200
\input amstex

\documentstyle{amsppt}
\NoBlackBoxes
%\NoPageNumbers
\pagewidth{16.5truecm}
\pageheight{22truecm}
\let\emptyset\varnothing
\let\eps\varepsilon

{\catcode`@=11
\gdef\nologo{\let\logo@\empty}
\catcode`@=12}
\nologo
%\hcorrection{.3in}

\centerline{ \bf  M725--Functional Analysis}
\vskip .05in
\centerline{\bf Homework-- Spring 2020}
\vskip .1in
\centerline{ Prof. Andrea R. Nahmod }
\vskip .4in

\document

Problems listed are from Brezis's Book. Note that each problem in the book has several parts. Do alll of them unless otherwise noted.
\vskip .2in

$\bullet$\, {\bf{Set 1. Due date: 02/13/2020}}
\vskip .2in

\underbar{Problems (from class)}:

\vskip .2in

\underbar{Problem 1}
Show that $p$ is sublinear iff $p$ is convex and $p(\alpha x)=\alpha p(x)$ for $\alpha\geq 0$

\vskip .1in 

\underbar{Problem 2}
Let
$$
P:=\bigg\{(Z,g) \, \, : \, \,  Z\subseteq X \text{ subspace }, Y\subset Z \text{ and } g:Z\to \Bbb{R} \text{ linear, } g\vert_Y=f  \text{ and }g \leq p \text{ on } Z\bigg\} $$
Endow $P$ with the following relation:
For $(Z_1,g_1),(Z_2,g_2)\in P$ let: 
$$
    (Z_1,g_1)\leq(Z_2,g_2) \, \iff \, Z_1\subseteq Z_2 \, \text{ and } \, g_2=g_1 \, \text{ on } Z_1
$$
Check that $\leq$ is a partial order in $P$.
\vskip .1in 

\underbar{Problem 3}
For $(Z_*,g_*)$ as defined in our proof of HB PartII (of an infinite-dimensional vector space), show that $Z_*$ is a subspace and that $g_*:Z_*\to\Bbb{R}$ is linear. Hence $(Z_*,g_*)\in P$.

\vskip .1in 

\underbar{Problem 4}
Prove Hahn-Banach Part II with $X$ being a normed space over $\Bbb{C}$ (instead of $\Bbb{R}$), where $p$ is the norm 

\vskip .1in 

\underbar{Problem 5} Let  $X$ be a normed vector space (n.v.s) and let $Y \subset X$ be a subspace. 
Define
$$  X^*:= \{x^*:X\to\Bbb{R}, \text{ linear and bounded} \} $$
$$    Y^*:=\{y^*:Y\to\Bbb{R}, \text{ linear and bounded}\} $$

(see Brezis pp. 3) Check that the {\it dual norm}, defined as:
$$
    \|x^*\|_{X^*}\, :=\, \sup_{x\in X : \| x\|_X<1} \, |x^*(x) | 
$$
is indeed a norm. Also check that $X^*\subseteq Y^*$.


\vskip .2in 

\underbar{Chapter 1}   \quad 1.1, 1.2, 1.3, 1.4, 1.5, 1.6, 1.7, 1.8.





\vskip .2in 

\underbar{Additional Problem}: Let $X$ be the vector space of all sequences $\{a_n\}_{n\geq 1} $of real numbers with only finitely many nonzero terms.
Consider the $\ell^1$-norm $\| \{a_n\} \|_1 = \sum_{n=1}^\infty  | a_n|$  and the $\ell^2$-norm, $\| \{a_n\} \|_2 =  \bigl(\sum_{n=1}^\infty  | a_n|^2 \bigr)^{1/2}$.  Prove that $\| \cdot  \|_1$ and $\| \cdot \|_2$ are {\bf not} equivalent norms.

\vskip .3in 



$\bullet$\, {\bf{Set 2. Due date: 03/26/2020}}
\vskip .2in

\underbar{Problems (from class)}:

\vskip .2in


\underbar{Problem 1}
    Let $(E, \| \cdot \|)$ be a n.v.s., and let $A\subset E$, $B \subset E$ be nonempty convex subsets. Assume $A$ is closed and $B$ is compact, and $A \cap B = \emptyset$, define
    $$
    C := A - B =\{ z \in C \, \, :\, \,  z = x -y, \quad x \in A, \, y \in B \, \} $$
    Prove that $C$ is closed.
\vskip .1in

\underbar{Problem 2}
    By Hahn-Banach (first geometric form), there exists a closed hyperplane that separates $B(0,r)$ and $C$. Then, there exists $f \in E^*$, nontrivial such that
  $$
    f(x-y) \leq f(rz), \quad \forall x \in A, \; \forall y \in B, \; \forall z \in B(0,1)
    $$
    Let
    $$
    \varepsilon := \dfrac{r}{2}\|{f}\|_{E^*} > 0
    $$
    Show that
    $$
    f(x) + \eps \leq f(y) - \eps, \quad \forall x \in A, \; \forall y \in B
    $$
    (equivalently, you can show that $f(x-y) \leq -r\|{f}\|$.)
\vskip .1in

\underbar{Problem 3}
    Consider Corollary 1.8 (Brezis pp. 8):
    \medskip
    
   {\bf Corollary}
    Let $F \subset E$ be a linear subspace such that $\overline{F} \ne E$. Then there exists some $f \in E^*$, $f \not\equiv 0$ such that
    $$
    \langle f,x \rangle = 0 \quad \forall x \in F
    $$
 \medskip
{\bf Remark}
    This corollary is useful to show that a linear subspace $F \subset E$ is dense in $E$. Then it'd suffice to show that every continuous linear functional on $E$ that vanishes on $F$ must vanish everywhere on $E$.

\medskip

    Show that the remark and corollary together imply the density of $F$ in $E$.

\vskip .1in
\underbar{Problem 4}
    Let $X,Y$ be Banach spaces. Let $T \colon X \to Y$ be bounded and linear. Show that if $T^*$ is invertible, then $T^*$ is open.
\vskip .1in

\underbar{Problem 5}
    Let $X,Y$ be Banach spaces. Let $T \in \Cal{L}(X,Y)$ such that $T^*$ is an injection with closed range. Prove that $T$ is surjective.

\vskip .2in
\underbar{Problem 6 (Class of 02/26/2020)}
ref. Brezis, pp 39, Theorem 2.12:

Assume that $T\in \Cal{L}(E,F)$  {surjective}. The following properties are equivalent:
\vskip .05in

(1) $T$ admits a right inverse
\vskip .05in

and 

\vskip .05in
(2)  $N(T)=T^{-1}(0)$ admits a complement in $E$

\vskip .1in
In the proof of (2)$\implies$(1): Let $L$ be a complement of $N(T)$. Let $P$ be the (continuous) projection operator from $E$ to $L$. Given $f\in F$, we denote by $x$ any solution of the equation $Tx=f$. Set $Sf=Px$ and note that $S$ is independent of the choice of $x$. It is easy to check that $S\in\Cal{L}(F,E)$ and that $T\circ S=I_F$.

\vskip .1in

{Explicitly check the last statement.}

\vskip .2in

\underbar{Problem 7 (Class of 03/03/2020)}
In the example: $E=F=\ell^1, E^*=\ell^\infty$, consider $A\in\Cal{L}(E,F)$ (linear, not necessarily bounded) such that $A: D(A)\to E$.

$$
    D(A)= \{  {\bold{x}}=(x_n)_{n\in\Bbb{N}}\in\ell^1:A(x_n)_{n\in\Bbb{N}}=n(x_n)\in\ell^1\}
$$
\vskip .1in
{Show that $D(A)$ is dense in $\ell^1$ and $A$ is closed.}


\vskip .2in
\underbar{Chapter 2 }: \quad  2.3, 2.4, 2.5, 2.6, 2.7, 2.8, 2.9, 2.10, 2.11, 2.12.

\vskip .3in

$\bullet$\, {\bf{Set 3. Due date: 04/28/2020}}

\vskip .2in
\underbar{Chapter 3}:  3.1, \, 3.3 (use HB in one direction), \, 3.5,  \,3.9, \, 3.10, \, 3.16 (1. and 2.), \, 3.18, \, 3.22

\vskip .2in

\underbar{Chapter 6:}  6.1, \,6.2, \, 6.3,  \, 6.7 1)2)4),  \, 6.8, \, 6.11. 


\enddocument


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\underbar{Chapter 2 Section 2.5}: \quad  1,  2,  5,  9,  15,  18.

\vskip .2in 

\underbar{Additional Problem 2}:   Let $a$ and $b$ be two positive real numbers. Let $x_0$ be a vector in a normed
space $X$. Assume that $|f(x_0)| \leq a$ for all $f \in X^{\ast}$  (= $X^{\prime}$) with $\|f\|_{X^{\ast}} \leq b$. Probe that $\|x_0\|_{X} \leq
\dfrac{a}{b}$


\vskip .3in 

{\underbar{Optional:}}  Do  23,  24 in Chapter 2 Section 2.5.

\vskip .3in

$\bullet$\, {\bf{Set 2. Due date: 04/04/2019}}
\vskip .1in
Note more problems will be added to this set soon so please start.
\vskip .2in
\underbar{Chapter 3 Section 3.8}: 1, 2, 4, 7,  8, 13, 15, 19, 25, 28. 
\vskip .3in

$\bullet$\, {\bf{Set 3. Due date: 04/30/2019}}

\vskip .1in
\underbar{Chapter 4 Section 4.5}:  1, 2, 3, 4, 5, 6, 8, 11, 13, 18, 22. 
\vskip .2in

\underbar{Hint for 1}:  prove sequential compactness.
\vskip .1in
\underbar{Hint for 11}: use Gram-Schmidt
\vskip .1in
\underbar{Hint for 18}. Consider a set $L= \{x_k\}_{k \geq 1}$ of normalized (to have norm one) linearly independent vectors in $X$ (infinite dimensional normed v.s). Consider the subspace Y of X consisting of all finite linear combination so of vectors in L. Next consider a sequence of functions $\{ h_{\ell}\}_{j \geq 1}$ defined on Y defined as $h_{\ell}(y) =  a \ell$\, \,  if $y= a x_{\ell}$ and zer otherwise and
let  $H(y) = \sum_{\ell=1}^{\infty}  h_{\ell} (y)$. Show that $H$ is well-defined in $Y$ but unbounded on the unit ball in $Y$.


\enddocument
\vskip .3in

$\bullet$\, {\bf{Set 4. Due date: 05/09/2019}}

\vskip .1in

\underbar{Chapters 5-6  }:  
\vskip .2in


\enddocument










\enddocument



                                               













