\magnification=1200
\input amstex
 
\documentstyle{amsppt}
%\vcorrection{1truein}
\pageheight{21truecm}
\pagewidth{15.5truecm}
\parskip 2pt plus 1pt minus 1pt
 
\NoBlackBoxes
 
\NoPageNumbers

\document
\baselineskip=12pt

\centerline{\bf Calculus for Life \& Social Sciences, I }

\centerline{\bf Math 127 \quad Section 2 \quad Fall 2004 }

\centerline{\bf Marc 131 }
\medskip
\centerline{\bf Prof. Andrea R. Nahmod }
\bigskip

\centerline{\bf Basic Ground Rules regarding Attendence and Sitting } 

\vskip .2in

This is a very large section with over 265 students enrolled. The
lecture hall where we will be having the lectures has some drawbacks.  
There are no doors at the back of the room. There is a constant background 'roar' 
from the ventilation system that makes the room's acoustics quite poor. 
Finally, the lightening is not very good and the projector screens and
whiteboards too small making it very difficult to see or read what's on 
them from the farthest rows of the lecture hall. . 

\vskip .1in

I will do everthing I can to overcome these shortenings. But I need
your help. So, here I am setting some basic rules to minimize any
disturbance during the lecture. I ask you to
observe them out of respect for your classmates. I will enforce them
out of basic fairness towards each and every student in the class. 

\vskip .1in

$\bullet$  All students are asked to sit within the first rows of the
classroom and preferably in the center block as long as there are
seats available. The last five rows should be left empty if at all
possible. In addition I ask
that you leave the first two or three rows {\bf at the side empty}. 

\vskip .1in 

$\bullet$ As you know, you are expected to attend {\bf every} class 
and actively participate in it. Please {\bf be on time}, a few minutes
earlier is preferable. You will not be allowed to enter the classroom 
if you are later than 15 minutes {\bf maximum}. If you are late you
are asked to enter quietly and sit down within the first three rows on
either side 'block' which are the closest to the entrance doors.  

\vskip .1in 

$\bullet$ I will do my best to finish sharply on time. Because of the
flow in any lecture ocassionally I might take an extra minute or two
and I apologize in advance for this. I will try to avoid it though. 
I ask you not to get up and start leaving {\bf before} I dismiss the
class. 

In addition, you are not allowed to leave {\bf early} unless you let 
me know in advance and have a valid reason. 
In such cases you are asked to sit at the {\bf begining of class} in the first three rows of the side-blocks, which are closer to either entrance-exit door. 

\vskip .1in

Many thanks in advance for your cooperation !  
\end 






