\magnification=1200
\input amstex

\documentstyle{amsppt}
\NoBlackBoxes
%\NoPageNumbers
\pagewidth{16.5truecm}
\pageheight{22truecm}

{\catcode`@=11
\gdef\nologo{\let\logo@\empty}
\catcode`@=12}
\nologo
%\hcorrection{.3in}

\centerline{ \bf  M534H   HOMEWORKS-- Spring 2008}
\vskip .1in
\centerline{ Prof. Andrea R. Nahmod }
\vskip .2in

\document

$\bullet$\, {\bf{Set 7. Due date:  Tuesday May 6  }}
\vskip .1in 
\underbar{Section 5.2} \, \, \,  3, 4, 7, 9, 10, 11, 17.

\vskip .1in 
\underbar{Section 5.3} \, \, \, 1, 2a)b), 3, 4a)b), 5a), 6, 10.

\vskip .1in 

\underbar{Section 5.4} \, \, \,  1, 5, 6, 7 , 8a)



\vskip .2in 

$\bullet$\, {\bf{Set 6. Due date:  Thursday April 24 }}
\vskip .1in 
\underbar{Section 4.3} \, \, \,   2, 4, 6, 11

\vskip .1in 
\underbar{Section 5.1} \, \, \, 3, 5, 6, 7, 9. 
\vskip .1in 

\underbar{Additional Problems for 4.3 and 5.1} 

\vskip .2in 

$\bullet$\, {\bf{Set 5. Due date:  Thursday April 10 }}

\vskip .1in

\underbar{Section 2.4}:\quad  1, 2, 7 (here you can use that the integral is $\sqrt{\pi}$ which we proved in class) 

\hskip 0.8in 8, 14, 15 16, 18

\vskip .1in 

\underbar{Section 2.5}:\quad 1  

\vskip .1in 

\underbar{Section 4.1}:\quad  2, 3
\vskip .1in 

\underbar{Section 4.2}:\quad  1, 3

\vskip .1in




\underbar{Additional Problems} Separate variables to solve the following problems. 
\vskip .1in 

A1.  \quad  $u_{tt} - u_{xx} =0$ in $0<x<3$ with boundary conditions $u(0, t)= u(3, t)=0$

\vskip .1in
A2. \quad $u_t=u_{xx}$ in $0<x< L$ with boundary conditions $u_x(0,t)= u (L,t)=0$

\vskip .1in

A3. \quad \, $u_t \,=\, u_{xx}\,+\, u$ in $0< x< \pi$ with boundary conditions $u(0,t)\, = \,u(\pi, t) \,=\,0$
\vskip .2in 

$\bullet$\, {\bf{Set 4. Due date:  Thursday March 13th }}

\vskip .1in


\underbar{Section 2.3}:\quad 2, 4, 5, 6, 7. 

\vskip .2in 
$\bullet$\, {\bf{Set 3. Due date:  Thursday March 6th.\, \underbar{Postponed to March 11th}}}

\vskip .1in

\underbar{Section 2.1}:\quad 1, 2, 5,  8, 9, 11  

\vskip .1in

{\bf Problem 11.}   Find the general solution of $$ 3u_{tt} +10 u_{xt} + 3 u_{xx} \, =\, \sin( x+t ) $$

\vskip .1in 

\underbar{Section 2.2}:  1, 2, 3, 5* 
\vskip .1in
{\bf Problem 5*}  \, Consider the wave equation in $1$D with {\it damping} 
$$ u_{tt} = c^2\, u_{xx} - k u - r u_{t} \, \qquad k, r >0$$  show that the {\it energy functional} $$E(t) \, =\, \frac{1}{2} \int_{-\infty}^{\infty} \, |u_t|^2  + c^2 |u_x|^2 + k |u|^2 \, dx $$ satisfies $dE/dt \le 0$; that is {\it energy decreases}. Assume $u$ and its derivatives vanish as  $x \to \pm \infty$. 

\vskip .1in

{\bf Additional Problems}.
\vskip .1in 
{\bf Problem A.1.} \,\, Find the solution to wave equation with initial conditions $u(x, 0) = \sin x, \, u_t(x, 0)= 0$. Calculate then $u_t(0, t)$. 

\vskip .1in

{\bf Problem A.2.}\, \, Solve the PDE \quad $ u_{xx} + u_{xt} -  10 u_{tt} \,=\, 0$



\vskip .2in


$\bullet$\, {\bf{Set 2. Due date:  Thursday February 28th }}
\vskip .2in

\underbar{Section 1.4}:  \quad  1

\vskip .1in 

\underbar{Section 1.5}:  \quad 1,  4,  5,  6 (modified; see below)

\vskip .2in 

\underbar{Problem 5 states}:  Consider the equation $$u_x + y u_y =0$$ 

with boundary condition $u(x,0)= \phi(x)$.

(a) \, For $\phi(x)= x$, for all $x$, show that no solution exists.

(b) \, For $\phi(x)=1$ for all $x$, show that there are many solutions. 

\vskip .1in

\underbar{Problem 6 states}:  Solve the equation $u_x \, +\, 2 x \, y^2\, u_y \,=\,0$ and find a solution that satisfies the auxiliary condition $u(0, y) =  y$.  

\vskip .2in 

\underbar{Section 1.6}:  \quad 1, 2, 4

\vskip .2in 
\underbar{Additional Problems:} 

(1) \, Find the general solution of $u_x - \sin(x)\, u_y \,=\,0$. 
Then find the special solution that satisfies $f(0, e^y)= e^{y}$.   

\vskip .1in

(2) \, Find the regions in 2d-space where $x^2\, u_{xx} + 4 u_{xy} +  y^2 \, u_{yy} \, =\,0$ 
is respectively elliptic, parabolic, hyperbolic. Plot these regions. 



\vskip .2in


$\bullet$\, {\bf{Set 1. Due date:  Thursday February 14th }}
\vskip .2in


\underbar{Section 1.1}:  \quad 2, 3, 4, 11

\vskip .1in 

\underbar{Section 1.2}:  \quad   2, 3, 4, 5.

\vskip .1in 

\underbar{Section 1.3}: \quad 7,  9,  10 (in $\Bbb R^3$), 11.

\vskip .2in 

\underbar{Additional Problem:}

\vskip .1in 
Let $u\,= \,u(\bold{x}, t)$ be a solution to the wave equation $u_{tt} - \Delta u =0$ in $\Bbb R^2$.  Assuming that $ \nabla u \to 0$ fast enough as $| \bold{x}| \to \infty$ prove that $$ E(t) \, =\, {\int}_{\Bbb R^2} \, \,  |u_t|^2 \, + \,  |\nabla\, u |^2 \, \, dx dy $$  is constant in $t$ for all time $t$. 

\enddocument



                                               
















\enddocument



                                               













