\magnification=\magstep1
\nopagenumbers          
\parindent=0pt          
\font\lbf=cmbx10 at 12pt
%%%%%%%    Variables    %%%%%%%%%%%%%%%%%%%%%%%%%%
\def\semester{ Spring 2003 }                              
\def\course{ Section 1 }
\def\time{T-Th 9:30 am  - 10:45 am.}
\def\room{LGRT 119 }
\def\instructor{Andrea R. Nahmod} 
\def\office{LRGT 1338}
\def\officephone{545- 6031}
\def\email{ nahmod\@math.umass.edu}
\def\Web{ http://www.math.umass.edu/$\sim ${nahmod}/624.html }
\def\officehours{ By appointment for now}
%%%%%\def\officehoursm { By appoint.}
\def\midtermone  {March 27th (TBC)}
\def\midtermtwo  {Saturday May 17th}
%\def\midtermthree{Thursday}
\def\homeworkValue{(40\%)}
\def\midtermValue{(30\% EACH)}
\def\finalValue{(30\%)} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\centerline{\lbf Math 624 - Real Analysis II}
\medskip
\centerline{\lbf \course \quad \semester}
\medskip
\centerline{\lbf \time\qquad \room}
\vskip.3in

%%% All material for following vbox defined above %%%%
{\vbox{\halign{#\hfil\quad&{\bf#}\hfil\qquad&#\hfil\quad&{\bf#}\hfil\cr
Instructor:&\instructor\cr
\noalign{\vskip9pt}
Office:&\office \cr
\noalign{\vskip9pt}
Te.: &\officephone \cr
\noalign{\vskip9pt}
E-Mail: &\email\cr
\noalign{\vskip9pt}
Course Webpage: &\Web\cr
\noalign{\vskip9pt}
Office Hrs:&\officehours \cr
\noalign{\vskip3pt}}}}
\bigskip

%%% All material for following vbox defined above %%%%
%{\vbox{\halign{#\hfil\quad&#\hfil\cr
%Recitation Section (with TA):&\uniqueone\cr}}} 
%\bigskip

The course will follow Gerald Folland's book : ``Real Analysis--
Modern Techniques and their Applications''. Second
Edition. Wiley-Intersciences Series (1999). 

\bigskip 
Your {\it Course Grade\/} will be determined on the basis of your:
\medskip

(1) {\bf Homework, Attendence and Class Participation} \homeworkValue
\vskip .05in

Homework will be assigned on a regular basis and 
will be collected bi-weekly. You must do all homework assigned in
class. Note that NO late homework will be accepted. 
Attendance and class participation are {\bf strongly} encouraged 
and will be taken into account {\it in conjunction} with your homework
average. The last assignment will be due on Tuesday May 14th. 
\medskip
{\bf Note: } In addition to the regular homework I will assign
throughout the semester and in
class some special {\it homeworks} -usually related to something we
are covering in class. You are {\bf required} to do them all and in a timely
fashion for the midterms exams will assume you have done so. 

(2) {\bf Exams} \midtermValue
\vskip .05in

Two exams will be held {\it outside class time} 
around the following dates (to be confirmed) : 
\medskip

\quad (a) \midtermone  \quad 
\qquad (b) \midtermtwo

\medskip

\end



