\magnification=\magstep1
\nopagenumbers          \parindent=0pt          \font\lbf=cmbx10 at 12pt
%%%%%%%    Variables    %%%%%%%%%%%%%%%%%%%%%%%%%%
\def\semester{ Fall 2001 }                              
\def\course{Math 131 H - Section 1}
\def\uniqueone  { U 1872515}
\def\uniquetwo {\quad Wednesdays \quad 12:20 pm -- 1:10pm \quad LGRT 111 }
\def\time{T-Th 11:15am -- 12:30 pm.}
\def\room{LGRT 319}
\def\instructor{Andrea R. Nahmod} 
\def\office{LRGT 1338}
\def\officephone{545- 6031}
\def\email{ nahmod@math.umass.edu}
\def\Web{ http://www.math.umass.edu/$\sim${nahmod}/131.html }
\def\officehours{ T 1 - 2 pm \& Th: 2:30 -3:30 pm}
\def\officehoursm { By appoint.}
\def\ta{Gregory Herring}
\def\taoffice{LGRT 1335 L}
\def\taofficehours{TBA}
\def\taofficehoursm{ By appoint. }
\def\taofficephone{545-9614.}
\def\taemail{herring@math.umass.edu}
\def\midtermone  {Thursday, October 16 } 
\def\midtermtwo  {Tuesday, December 4  }
\def\midtermthree{Wednesday November 14}
%\def\quizlocation{BATTS 7}
%\def\quiztime{ }
\def\finaldate{TBA} 
%\def\finaltime{9:00- 12:00 noon} 
\def\homeworkValue{(20\%)}
\def\midtermValue{(20\% EACH)}
\def\finalValue{(20\%)} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\centerline{\lbf Honors Calculus I - \semester}
\medskip
\centerline{\lbf \course \quad \uniqueone}
\medskip
\centerline{\lbf \time\qquad \room}
\vskip.3in

%%% All material for following vbox defined above %%%%
{\vbox{\halign{#\hfil\quad&{\bf#}\hfil\qquad&#\hfil\quad&{\bf#}\hfil\cr
Instructor:&\instructor&TA:&\ta\cr
\noalign{\vskip9pt}
Office:&\office &Office:&\taoffice\cr
\noalign{\vskip9pt}
Te.: &\officephone &Te.: &\taofficephone\cr 
\noalign{\vskip9pt}
E-Mail: &\email &E-mail:&\taemail\cr
\noalign{\vskip9pt}
Office Hrs:&\officehours &Office Hrs:&\taofficehours\cr
\noalign{\vskip3pt}
Also : &\officehoursm & Also: &\taofficehoursm \cr}}}
\bigskip

%%% All material for following vbox defined above %%%%
{\vbox{\halign{#\hfil\quad&#\hfil\cr
Recitation Section (with TA):\uniquetwo\cr}}} 
\bigskip
{\bf Course Webpage}:  http://www.math.umass.edu/$\sim${nahmod}/131.html 

\bigskip 

Your {\it Course Grade\/} will be determined on the basis of your:
\medskip

(1) {\bf Homework, Attendence and Class Participation} \homeworkValue
\vskip .05in

Homework will be assigned on a daily basis and 
will be collected once a week generally on Thursdays in class
and returned to you generally by the following Tuesday. 
NO LATE HOMEWORK will be accepted.
YOU MUST DO ALL HOMEWORK PROBLEMS ASSIGNED IN CLASS. This 
 $20 \% $ of your final grade will be based on your homework final average, 
and on your attendence and class participation 
in {\it both} the lectures and the recitations (with your TA). 

\medskip

(2) {\bf Midterm Exams and Symbolic Test :} \midtermValue
\vskip .05in

Two midterm exams (a) and (b) and a Symbolic (Derivative) Test (c) will be held during the 
semester on the following days (subject to slight changes). 
\medskip

\quad (a) \midtermone
\quad (b) \midtermtwo
\quad (c) \midtermthree
\medskip

The two midterm exams will be held between 6:00 pm and 8:00pm in a location
to be announced. The symbolic test will be administered by your TA and
will be held in your recitation section. Note
that NO CALCULATORS will be permitted on the {\it symbolic test}.

Please make a note of these dates and times so that you make 
every effort to be available for them. 

\medskip
(3) {\bf Final Exam:} \finalValue 
\vskip .05in

The Final Exam will be held on a date and time to be announced. Note that
the last day of finals is December 22, 2001. Snow date December 24, 2001.
This will be a comprehensive exam. 



\end



